### 2012-03-16 doc/theses/mikula/pre_creation_of_algorithm.tex
Master thesis: In progress.

\chapter{Pre-creation of Algorithm}
According to the analysis in the previous chapter, there is quite a wide range of possible utilizations of XQuery queries. Besides analysis of what information can be extracted from queries, it is needed to devise how the queries will be processed. This chapter discusses some questions and issues that emerged in an early phase of the algorithm fabrication.

>>>>

\chapter{Pre-creation of Algorithm} \label{CHAPTER_precreation_of_algorithm}
According to the analysis in the previous chapter, there is quite a wide range of possible utilizations of XQuery queries. Besides analysis of what information can be extracted from queries, it is needed to devise how the queries will be processed. This chapter discusses some questions and issues that emerged in an early phase of the algorithm fabrication.
